Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-28 paper/main.tex
bit of text

%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Syntax Is All You Need: A Universal-Language\\Approach to Mutant Generation}

@@

Our approach also makes introducing advanced techniques such as
Trivial Compiler Equivalence (TCE) into a mutation workflow easy.
While we support TCE for some languages inside the tool, a user can
always write a simple script to check...

@@

In addition to these core research questions, evaluated over six files
from six real-world projects for four languages, we also present a
case study, applying our implementation to a program in a language for
which it has no rules, Haskell.

@@

\begin{table}[hbtp]
  \centering
  \caption{Overview of Mutation Testing Tools. universalmutator has singificantly fewer lines of code than any of the single language tools.}
  \label{tab:mutationtools}

@@

>>>>

%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Syntax Is All You Need: A Universal-Language Approach to Mutant Generation}

@@

We implemented our approach in a mutation testing tool, written in
about 2,200 lines of Python.  The rules defining mutation operators
for a set of languages including C, C++, Python, Java, Lisp, Swift,
Rust, Solidity, Fe, Vyper, JavaScript, and Go, required another 436
lines; this is the total for comby and regexp-based rules, so each
version requires only 218 lines of rule definitions.

While many tools provide a GUI front-end, or integrate to a particular
testing library, we chose to focus on an easily configured CLI,
allowing a user to specify the commmands used to build mutants or
run tests.  While less convenient in the case where there is a good
fit between a tool's integrations and a project's environment, we
found this flexibility useful even when limiting considerations to a
single language.  For example, the widely used PIT system is strongly tied to
certain versions of JUnit, and mutating projects using a different
testing infrastructure, or an older JUnit, can be difficult.  Our
approach also is suitable for use in CI and other automated environments.

For the most part we expect users to provide build commands, but do
support automatic compilation and comparison of mutants for Python,
Solidity, Fe, Vyper, Swift, Rust, and Java, including Trivial Compiler
Equivalence \cite{TCE} checks for redundancy of mutants.  These
default handlers can always be over-ridden if they do not work with a
particular build setup.

Our tool has been available as an open source project on GitHub and
available for installation via Python pip for
some time, has received contributions from users not involved in
our project, and been adopted by at least one very large project as
the officially recommended mutation tool.  We omit details for
purposes of blinding.

@@

Both research questions were addressed by generating and running
mutants for a set of four programming languages: C++, Java, Python,
and Rust.  We picked six projects with 1) a large number of GitHub
stars and 2) an easy-to-execute, passing test suite for each language,
and then chose the largest source file below 20KB in size from each project to mutate.  Limiting
mutation to one large but not extremely large file made is easier to compare generated mutants and
manually inspect for mutant equivalency.  The only bias to file
selection was size, which we do not believe should affect our results
significantly.

We additionally present a small
case study, applying our implementation to a program in a language for
which it has \emph{no} rules, Haskell.

@@

@@

\begin{table}[hbtp]
  \centering
  \caption{Overview of Mutation Testing Tools.}
  \label{tab:mutationtools}

Table \ref{tab:mutationtools} shows the set of tools compared.  We
attempted to identify well-maintained and commonly used tools for each
language chosen.
